---
title: "R Package installation"
author: "Darawan Rinchai"
date: "10/15/2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R Package installation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,eval = FALSE)
```

### Requirment packages for modular repertoire analysis using "BloodGen3Module"

## OPTION 1: Assumed packages had been intalled into your R
## If these packages already installed in your R, then you can simply load all those pacakges using function library()

```{r pressure, echo=TRUE}
library(BloodGen3Module)
library(ComplexHeatmap)
library(ggplot2)
library(reshape2)
library(gtools)
library(matrixStats)
library(preprocessCore)
library(randomcoloR)
```


## OPTION 2: Assumed that the packages have not been installed in your R

##This is an R function that will help to install and load the required packages

## Function for intallation and loading packages from CRAN

```{r create a functiona for installation and loading R packages from CRAN,echo = TRUE}
iCRANpak <- function(required.packages){
  required.packages <- c(required.packages,"BiocManager")
  missing.packages <- required.packages[!(required.packages %in% installed.packages()[,"Package"])]
  if(length(missing.packages)) {install.packages(missing.packages, dependencies = TRUE)}
  invisible(sapply(required.packages, library, character.only = TRUE))
}

```

## Function for intallation and loading packages from Bioconductor

```{r creat a function for installation and loading R packages from Bioconductor,echo = TRUE}
iBIOpak <- function(required.bioconductor.packages){
  missing.packages <- required.bioconductor.packages[!(required.bioconductor.packages %in% installed.packages()[,"Package"])]
  if(length(missing.packages)) {BiocManager::install(missing.packages)}
  invisible(sapply(required.bioconductor.packages, library, character.only = TRUE))
}
```

## Simply add required package to each functions

```{r installation and loading packages,echo = TRUE}
required.packages = c("ggplot2","reshape2","ggplot2","gtools","matrixStats","preprocessCore","randomcoloR")
required.bioconductor.packages = "ComplexHeatmap"

iCRANpak(required.packages)
iBIOpak(required.bioconductor.packages)

```



